Positivity-Preserving Adaptive Runge--Kutta Methods

### 2021-03-01 nusslein_vsrp/latex/overview.tex
Rephrase explanation about efficiency.

>>>>

\linelabel{line:cost}\revA{
It is natural to ask whether the adaptation of the weights through the algorithm proposed
here is more efficient than simply using a smaller step size.  For this problem that can
be discretized explicitly with a right-hand-side that is relatively cheap to evaluate,
using a smaller step size is
generally more efficient, at least with the current un-optimized implementation of the LP
solution.  For problems where implicit time integration is necessary, or with a more computationally
expensive derivative evaluation, the LP approach may be more efficient, especially if
the implementation were optimized.  This kind of optimization is the subject of future work.
}
